animbook: Visualizing changes in performance measures and demographic affiliations using animation

### 2023-10-27 animbook-journal.Rmd
small changes to intro paragraph

The concept of "zombie companies" began to attract attention when an article on the proliferation of zombie companies (@zombie_companies_2008). The "zombie companies" are generally defined as companies with an interest coverage ratio of less than one for a period of more than three years. These companies are taking space in the market but adding no life to the economy. There could be other movement patterns, beyond zombies, that are interesting, such as companies that suddenly become very successful, or in politics voters who switch party affiliation between elections. Viewing changes between categories over time is an interesting challenge for visualization.

  The New York Times provided a possible solution in the article "Extensive data show punishing reach of racism for black boys" (@the_new_york_time) to tell the story of how racism appears to inhibit socioeconomic change. This approach can be adapted to address the zombie problem by capturing the movement between groups over a specific period.

>>>>

The concept of "zombie companies" began to attract attention when @zombie_companies_2008 reported on their proliferation in Japan. Zombie companies are defined as those with an interest coverage ratio of less than one for a period of more than three years, that is, companies taking space in the market but adding no life to the economy. We would detect their presence by a drop in performance, which is a movement pattern in their relative ranking over time. Generally, studying movement patterns is interesting for many problems, including rocket ship startups that rapidly perform well, or in politics, to study voters who switch party affiliation between elections. Viewing changes between categories over time is an interesting challenge for visualization.

The New York Times provided a possible solution in the article titled "Extensive data show punishing reach of racism for black boys" (@the_new_york_time) to tell the story of how racism appears to inhibit socioeconomic change. This animation is the motivation for the new visualization presented here, to be applied generally.
